Compare pseqs

### 2019-05-17 comparepseqs.Rmd
Missing commas

```{r libraries}
library(dplyr)
library(tibble)
library(phyloseq)
library(microbiome)
library(parallel)
library(knitr)
library(gridExtra)
```

@@

 ```{r adonis calculation}
 if (!file.exists("rds-comparepseqs/beta.diversity.rds")) {
     covariates.min <- c("BL_AGE", "SEX")
     covariates.full <- c("BL_AGE", "SEX", "BMI", "CURR_SMOKE",
                          "Q57X", "BL_USE_RX_C03", "BL_USE_RX_C07",
                          "BL_USE_RX_C08", "BL_USE_RX_C09")

     betadiversity <- mclapply(c2l(names(pseq)), function(x)
         list(min = calculateadonis(dset = meta(pseq[[x]]),
                                    matrix = bray.dist.matrix[[x]],
                                    covariates = covariates.min,
                                    npermutations = 1000),
              full = calculateadonis(dset = meta(pseq[[x]]),
                                           matrix = bray.dist.matrix[[x]],
                                           covariates = covariates.full
                                           npermutations = 1000)
         mc.cores = length(pseq))
     saveRDS(betadiversity, file = "rds-comparepseqs/beta.diversity.rds")
    } else {
     betadiversity <- readRDS("rds-comparepseqs/beta.diversity.rds")
}
```

```{r plot alpha diversity, eval = FALSE}
beta.min <- lapply(c2l(names(pseq)), function(x) {
    alpha.min[[x]] %>% mutate(R2 = 0) %>% select(model_name, R2, response)
})

>>>>

```{r libraries}
library(dplyr)
library(tibble)
library(phyloseq)
library(microbiome)
library(parallel)
library(knitr)
library(gridExtra)
library(vegan)
```

@@

 ```{r adonis calculation}
bray.dist.matrix %>% str

 if (!file.exists("rds-comparepseqs/beta.diversity.rds")) {
     covariates.min <- c("BL_AGE", "SEX")
     covariates.full <- c("BL_AGE", "SEX", "BMI", "CURR_SMOKE",
                          "Q57X", "BL_USE_RX_C03", "BL_USE_RX_C07",
                          "BL_USE_RX_C08", "BL_USE_RX_C09")

     betadiversity <- mclapply(c2l(names(pseq)), function(x)
         list(min = calculateadonis(dset = meta(pseq[[x]]),
                                    matrix = bray.dist.matrix[[x]],
                                    covariates = covariates.min,
                                    npermutations = 1000),
              full = calculateadonis(dset = meta(pseq[[x]]),
                                           matrix = bray.dist.matrix[[x]],
                                           covariates = covariates.full,
                                           npermutations = 1000),
              mc.cores = length(pseq)))
     saveRDS(betadiversity, file = "rds-comparepseqs/beta.diversity.rds")
    } else {
     betadiversity <- readRDS("rds-comparepseqs/beta.diversity.rds")
}
```

```{r plot alpha diversity, eval = FALSE}

betadiversity
beta.min <- lapply(c2l(names(pseq)), function(x) {
    alpha.min[[x]] %>% mutate(R2 = 0) %>% select(model_name, R2, response)
})
